%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {ZS} % Organization
    {Data Engineer (BTSA)} % Job title
    {New Delhi, India} % Location
    {Aug 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing and delivering data warehousing solutions using AWS EMR, Apache Spark for analyzing and interpreting real world data to empower a successful venture.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Triveous Technologies Private Limited} % Organization
    {Software Development Engineer Intern} % Job title
    {Bangalor, India (Remote)} % Location
    {May 2020 - Sept. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented multiple event-driven API microservices in Node.js NestJS and managed their deployments on AWS ECS.}
        \item {Built a scalable notification delivery system using Redis, FCM, AWS SNS, SES and SQS.}
        \item {Spin up a cost-effective, automated GitLab Runner setup on AWS that scales in/out on demand and also offers the possibility to switch off the entire stack at predefined time intervals to save costs.}
        \item {Implemented an image-caching service supporting on-demand crop, resizing and flipping of images while serving.}
        \item {Built an automated status-page for multiple services using Atlassian Statuspage, AWS Cloudwatch Events and Lambda.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Solve Foundation (Intellify/Indian Road Safety Campaign)} % Organization
    {Technical Mentor} % Job title
    {New Delhi, India} % Location
    {Jan. 2020 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mentored development of online web-portal and mobile application for National Science and Creativity Program (NSCP).}
        \item {Assisted the team in the design, implementation and debugging processes in all aspects of front-end, back-end, APIs, android or deployments.}
        \item {Designed a development methodology to smoothen the development-process of Intellify making it more efficient and trackable.}
        \item {Managed the complete source-code version-control for proper code reviews and merges of any fixes, updates and features.}
        \item {Setup analytics for tracking and reporting NSCP website traffic that provided in-depth detail about visitors on the website.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intellify, Internship} % Organization
    {Python \& Web Developer Intern} % Job title
    {New Delhi, India} % Location
    {May 2019 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented an user-based collaborative-filtering online quiz-recommendation system for The International Science and Creativity Olympiad (ISCO).}
        \item {Implemented REST API using Python for compiling, analysing and presenting the results of students and  schools for all rounds in ISCO.}
        \item {Designed and implemented front-end web-pages for Intellify website and exam portal using Bootstrap framework.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bytescare} % Organization
    {Software Development Engineer Intern} % Job title
    {Noida, India (Remote)} % Location
    {Mar. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Automated the process of privacy data collection and take-down procedures for content creators.}
        \item {Built a mail-caching, monitoring and processing system as REST API using Node.js, that processes all emails for a take-down request, applying NLP algorithm implemented using Python and Natural Language Toolkit (NLTK).}
        \item {The NLP algorithm along with other modules is used to classify the type of response for a take-down request email and monitor the mail conversation for every request.}
        \item {The algorithm for language processing is similar to sentiment-analysis but is customized to work with emails and uses a corpus of approximately 1,00,000 formal/informal and positive/negative responses.}
      \end{cvitems}
    }
\end{cventries}
