%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Triveous, Bangalore India} % Organization
    {Software Development Engineer Intern} % Job title
    {Remote} % Location
    {May 2020 - Sept. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented multiple API microservices in Node.js NestJS following event-driven architecture and managed their deployments on AWS ECS.}
        \item {Built a scalable notification delivery service using Redis, FCM, AWS SNS, SES and SQS.}
        \item {Spin up a cost-effective, automated GitLab Runner setup that scales in/out on demand and also offers the possibility to switch off the entire stack at predefined time intervals to save costs.}
        \item {Implemented an image-caching server, to cache all images served by multiple clients and allow on-demand crop, resizing and flipping of images.}
        \item {Built a fully automated status-page for multiple services using Atlassian Statuspage, AWS Cloudwatch Events and Lambda.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Solve Foundation (Intellify/Indian Road Safety Campaign), New Delhi India} % Organization
    {Technical Mentor} % Job title
    {New Delhi, India} % Location
    {Jan. 2020 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mentored development of online web-portal and mobile application for National Science and Creativity Program (NSCP).}
        \item {Assisted the team in the design, implementation and debugging process whenever they felt stuck with something, irrespective whether in the front-end, back-end, APIs, android (mobile) or deployments.}
        \item {Managed the complete source-code version-control myself, to take care of all the conflicts and ensure proper merges of fixes, updates and features.}
        \item {Came up with an improved development methodology that was adopted by Intellify to smoothen the development-process, making it more efficient and trackable at the same time.}
        \item {Setup analytics for tracking and reporting NSCP website traffic that provided in-depth detail about visitors on the website.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intellify, New Delhi India} % Organization
    {Technical Intern (Python/Web Developer)} % Job title
    {New Delhi, India} % Location
    {May 2019 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented an user-based collaborative-filtering quiz-recommendation system for online quiz platform of the International Science and Creativity Olympiad (ISCO).}
        \item {Implemented REST API using Python for compiling and analysing the results for schools and students for all rounds in ISCO.}
        \item {Developed REST APIs, to present the result statistics on dashboards for the web-portal and mobile application.}
        \item {Designed and implemented front-end web-pages for Intellify website and exam portal using Bootstrap framework.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bytescare, Noida India} % Organization
    {Software Development Engineer Intern} % Job title
    {Remote} % Location
    {Mar. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Automated the process of privacy data collection and take-down procedures for content creators.}
        \item {Built a mail-caching, monitoring and processing system as REST API using Node.js, that processes all emails for a take-down request, applying NLP algorithm implemented using Python and Natural Language Toolkit (NLTK).}
        \item {The NLP algorithm along with other modules is used to classify the type of response for a take-down request email and monitor the mail conversation for every request.}
        \item {The algorithm for language processing is similar to sentiment-analysis but is customized to work with emails and uses a corpus of approximately 1,00,000 formal/informal and positive/negative responses.}
      \end{cvitems}
    }
\end{cventries}
